Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      else{new_status[j] <- 'S'}

      }

      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)

>>>>

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}
